---
title: "Trump"
author: "Kejing Li"
date: "11/17/2019"
output: github_document
---

```{r setup, echo = TRUE}
library(tidyverse)
library(broom)
library(modelr)
```

```{r import}
#import the data
trump_data <- read_csv("data/trump.csv")
```

# Q1
## Estimate a basic (single variable) linear regression model of the relationship between the importance of the video and feelings towards Donald Trump.
```{r}
#construct linear model
trump_mod <- lm(trump ~ video, data = trump_data)
tidy(trump_mod)
```

## Calculate predicted values
```{r}
trump_predict <- augment(trump_mod,
                     newdata = data_grid(trump_data, video))
trump_predict
```

## graph the relationship between the two variables using the predicted values, and determine whether there appears to be a significant relationship.

```{r}
ggplot(trump_data, aes(video)) +
  geom_point(aes(y = trump)) +
  geom_line(aes(y = .fitted), data = trump_predict, color = "red", size = 1) +
  geom_point(aes(y = .fitted), data = trump_predict, color = "blue", size = 3)
```

__Answer:__ From the above estimation, there appears to be a significant relationship for two reasons:

1. The model's p-value is 0, which indicates significance.
1. It can be learned from the above graph that the more people care about the video, the lower their feeling thermometer ratings of trump will be expected. 


```{r, echo = TRUE}
devtools::session_info()
```
